Comparison among doublet predictions on benchmarking datasets

### 2024-07-02 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd
move vectors out of maps, and use one mutate

      dataset_df |>
        dplyr::rowwise() |>
        # Add column `consensus_call`
        #  "doublet" if all three methods are doublet, and "singlet" otherwise
        dplyr::mutate(
          consensus_call = dplyr::if_else(
            all(c(scdbl_prediction, scrublet_prediction, cxds_prediction) == "doublet"),
            "doublet", 
            "singlet"
          )
        ) |>
        # Add column `consensus_class`
        #  "doublet" if all three methods are doublet, "singlet" if all three methods are singlet, 
        #  and "ambiguous" if there are any disagreements
        dplyr::mutate(
          consensus_class = dplyr::case_when(
            consensus_call == "doublet" ~ "doublet",
            all(c(scdbl_prediction, scrublet_prediction, cxds_prediction) == "singlet") ~ "singlet", 
            .default = "ambiguous"
          )
         ) |>
        # Add column `confusion_call`
        #  tp/tn/fp/fn based on the `consensus_call` column
        dplyr::mutate(
          confusion_call = dplyr::case_when(
            consensus_call == "doublet" && ground_truth == "doublet" ~ "tp",
            consensus_call == "singlet" && ground_truth == "singlet" ~ "tn",
            consensus_call == "doublet" && ground_truth == "singlet" ~ "fp",
            consensus_call == "singlet" && ground_truth == "doublet" ~ "fn"
          )
        )
      }
  ) 
```

@@

```{r, fig.width = 12, fig.height = 6}
doublet_df_list |>
  purrr::imap(
    \(df, dataset) {

      pc_color_columns <- c("scDblFinder prediction" = "scdbl_prediction",
                            "scrublet prediction" = "scrublet_prediction",
                            "cxds prediction" = "cxds_prediction",
                            "Ground truth" = "ground_truth", 
                            "Consensus call" = "consensus_call")

@@

```{r, fig.width = 12, fig.height = 6}
doublet_df_list |>
  purrr::imap(
    \(df, dataset) {

      pc_color_columns <- c("scDblFinder prediction" = "scdbl_prediction",
                            "cxds prediction" = "cxds_prediction",
                            "Ground truth" = "ground_truth", 
                            "Consensus call" = "consensus_call")

>>>>

      dataset_df |>
        dplyr::rowwise() |>

        dplyr::mutate(
          # Add column `consensus_call`
          # "doublet" if all three methods are doublet, and "singlet" otherwise          
          consensus_call = dplyr::if_else(
            all(c(scdbl_prediction, scrublet_prediction, cxds_prediction) == "doublet"),
            "doublet", 
            "singlet"
          ),
          # Add column `consensus_class`
          #  "doublet" if all three methods are doublet, "singlet" if all three methods are singlet, 
          #  and "ambiguous" if there are any disagreements
          consensus_class = dplyr::case_when(
            consensus_call == "doublet" ~ "doublet",
            all(c(scdbl_prediction, scrublet_prediction, cxds_prediction) == "singlet") ~ "singlet", 
            .default = "ambiguous"
          ), 
          # Add column `confusion_call`
          #  tp/tn/fp/fn based on the `consensus_call` column
          confusion_call = dplyr::case_when(
            consensus_call == "doublet" && ground_truth == "doublet" ~ "tp",
            consensus_call == "singlet" && ground_truth == "singlet" ~ "tn",
            consensus_call == "doublet" && ground_truth == "singlet" ~ "fp",
            consensus_call == "singlet" && ground_truth == "doublet" ~ "fn"
          )
        )
      }
  ) 
```

@@

```{r, fig.width = 12, fig.height = 6}
pc_color_columns <- c("scDblFinder prediction" = "scdbl_prediction",
                      "scrublet prediction" = "scrublet_prediction",
                      "cxds prediction" = "cxds_prediction",
                      "Ground truth" = "ground_truth", 
                      "Consensus call" = "consensus_call")
doublet_df_list |>
  purrr::imap(
    \(df, dataset) {

@@

```{r, fig.width = 12, fig.height = 6}
pc_color_columns <- c("scDblFinder prediction" = "scdbl_prediction",
                      "cxds prediction" = "cxds_prediction",
                      "Ground truth" = "ground_truth", 
                      "Consensus call" = "consensus_call")

doublet_df_list |>
  purrr::imap(
    \(df, dataset) {
